### 2019-05-01 tii/tex/optimization.tex
Submit version v1.1

To handle this corner case, we introduce another methodology, named \emph{weighted reservoir sampling}, as a substitution of linear regression. 
Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
After that, the map function is called locally to process the sampled data (\textit{Sampling} in Figure \ref{fig:shuffle}). 
Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
Note that sampling does not consume the input data of map tasks. 
The $BlockSize_{ji}$ can be calculated by:
\begin{equation}
\label{equationsample}
\begin{aligned}
	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
	sample_i &= \text{number of samples for $reduce_i$}
\end{aligned}
\end{equation}
% The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example. 
Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
On the other hand, the result of linear regression comes out with a large relative error. 
Though the weighted reservoir sampling is precise, it also introduces extra overhead. 
We will show the overhead evaluation of sampling in Section \ref{evaluation}.
% {\color{black}
% Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
% We will show the overhead evaluation of sampling in Section \ref{evaluation}. 
% }

>>>>

To handle this corner case, we introduce another methodology, named \emph{weighted reservoir sampling}, as a substitution of linear regression. 
Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
After that, the map function is called locally to process the sampled data (\textit{Sampling} in Figure \ref{fig:shuffle}). 
Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
Note that sampling does not consume the input data of map tasks. 
The $BlockSize_{ji}$ can be calculated by:
\begin{equation}
\label{equationsample}
\begin{aligned}
	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
	sample_i &= \text{number of samples for $reduce_i$}
\end{aligned}
\end{equation}
% The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
% In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
% The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example. 
% Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
% On the other hand, the result of linear regression comes out with a large relative error. 
% Though the weighted reservoir sampling is precise, it also introduces extra overhead. 
% We will show the overhead evaluation of sampling in Section \ref{evaluation}.
% {\color{black}
Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
We will show the overhead evaluation of sampling in Section \ref{evaluation}. 
% }
